%This is a Tex Version of cis730 homework
\documentclass{amsart}
\setlength{\textheight}{9.15in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}  
\usepackage[export]{adjustbox}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{framed}
\usepackage{enumitem}
\newcounter{temp}
\theoremstyle{definition}
\newtheorem{Thm}{Theorem}
\newtheorem{Prob}{Problem}
\newtheorem*{Def}{Definition}
\newtheorem*{Ans}{Answer}
\newcommand{\dis}{\displaystyle}
\newcommand{\dlim}{\dis\lim}
\newcommand{\dsum}{\dis\sum}
\newcommand{\dint}{\dis\int}
\newcommand{\ddint}{\dint\!\!\dint}
\newcommand{\dddint}{\dint\!\!\dint\!\!\dint}
\newcommand{\dt}{\text{d}t}
\newcommand{\dA}{\text{d}A}
\newcommand{\dV}{\text{d}V}
\newcommand{\dx}{\text{d}x}
\newcommand{\dy}{\text{d}y}
\newcommand{\dz}{\text{d}z}
\newcommand{\dw}{\text{d}w}
\newcommand{\du}{\text{d}u}
\newcommand{\dv}{\text{d}v}
\newcommand{\ds}{\text{d}s}
\newcommand{\dr}{\text{d}r}
\newcommand{\dth}{\text{d}\theta}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\bbQ}{\mathbb{Q}}
\newcommand{\bbZ}{\mathbb{Z}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\dd}[2]{\dfrac{\text{d}#1}{\text{d}#2}}
\newcommand{\dydx}{\dfrac{\text{d}y}{\text{d}x}}
\renewcommand{\labelenumi}{{\normalfont \arabic{enumi}.}}
\renewcommand{\labelenumii}{{\normalfont \alph{enumii}.}}
\renewcommand{\labelenumiii}{{\normalfont \roman{enumiii}.}}
\font \bggbf cmbx18 scaled \magstep2
\font \bgbf cmbx10 scaled \magstep2
\usepackage{fancyhdr}
\usepackage{lipsum}
\def\res{\mathop{Res}}
\fancyhead{}
\fancyfoot{}
\rfoot{\thepage}
\fancyhf{}
\pagestyle{fancy}
\begin{document}


% HEADER INFO
\noindent
\LARGE{\textbf{CIS-730: Artificial Intelligence}} \\
\large
\noindent
\textbf{Problem Set 1} \\
Fall 2018 \\
Homework 1 of 10: Problem Set (PS1) \\
Warm-up: Intelligent Agents, Search \\
Assigned: Mon 20 Aug 2018 \\
Due: Wed 29 Aug 2018 on-campus, Fri 31 Aug 2018 distance (before midnight) \\
Solution by:  John Boyington \\
\newline
\bigskip



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Problem 1: (530/730) Perception and rationality.} \\

Continuing the class discussion from Lecture 1 (“Intelligent Agents” – slide 0 of Lecture 0, slide 4 of Lecture 1):
Consider voice-operated home assistant or smart home appliance as the agent to discuss.
What limitations of this agent’s sensors (instruments for collecting perceptual information) limit its view of the world?
How does this impact its rationality? Give at least two concrete examples of the effects of sensor error and limitations.
You may use measurement error and data processing error as effects, but specify which type you are writing about.
\vspace{0.05\textheight}

\noindent
\textbf{Solution:}

1. When trying to listen to someone in another room, the audio sensor may not be able to pick up that person's voice and distinguish it from the noise inherent in the signal. Unable to hear the person, the agent may rationalize that it's not currently being spoken to and remain idle, which is not true.

2. Depending on the quality of the microphone used to pick up an audio signal, a person speaking extremely close to the microphone or yelling at it might exceed the limitation of the microphone. This may cause the audio signal to be heavily distorted and be impossible for the agent to abstract particular words or phrases from the signal.

\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Problem 2: (530/730) Types of agents.} \\
Consider the five term project domains discussed in class:
\begin{enumerate}[label=\alph*]
\item) ontology or other description logic reasoning task [Task 3 in Lecture 0, Slide 26]
\item) cybersecurity task [Task 4]
\item) conversational agent or cognitive service-based question-answering (QA) agent [Task 5]
\item) image processing (especially style transfer) or vision task [Task 6]
\item) expert system or analogical reasoning task [Task 7]
\item) AI for social good [Task 8]
\item) dynamic robot path planning problem [Task 1]
\item) reinforcement learning and/or deep learning task for game playing agent [Task 2]
\end{enumerate}
(The first two topics are the oldest and are due to be retired for at least a few years after this course; the third and fourth topic is in its second year and will be offered again next year, and the last four are new or newly relaunched topics.)

Give an example of two agents for one of these domains to illustrate the distinction between
a reflex agent with state and a goal-based or preference-based agent. Hint: take a look at AItopics.org and examples of test beds and agents such as:

For task category (b): DARPA Cyber Grand Challenge – http://archive.darpa.mil/cybergrandchallenge/, https://github.com/CyberGrandChallenge/

For task category (c): see the Alexa Prize – https://developer.amazon.com/alexaprize

For task category (f) games: see OpenAI Gym – https://gym.openai.com (including DOTA2 and Atari games), VizDOOM, Roguelike games, AI Birds


\bigbreak

\textbf{Solution:}

[Task 2]
An tic-tac-toe playing agent could in theory have a lookup table for each move after observing the state of the world.
This is a reflex behavior.
In theory, it could always make a move that would lead to either a win or a draw without actually deliberating about a goal.

HeartyTianSim, a goal-based agent developed by the Eagle's Wings team from Canada was used to win an AIBIRDS competition.
The agent would simulate 120 initial launches and assess things like the number of enemies destroyed and structural damage or change.
This goal-based approach seeks to maximize the score one would receive on this game, which involves deliberating about choice, not just reacting.



\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Problem 3: (530/730) State space representation.} \\
(Adapted from Section 3.1, Russell \& Norvig 3e, and Poole \& Mackworth, 2e.) Consider a delivery robot of the kind discussed in Poole and
Mackworth 2e (see http://artint.info/html/ArtInt\_48.html for an example and excerpt).

Specify a state space for the following two tasks:
\begin{enumerate}
\item 8-puzzle vs. N-queens. Read about the 8-puzzle in Section 3.2.1 of Russell and Norvig, 3 rd edition (p. 70-71).
Discuss differences in combinatorial complexity of the state space and simplifying properties such as symmetry – which problem
exhibits these properties and which do not?
What are some challenges in checking state spaces using generate-and-test?
(We will come back to this when we discuss constraint satisfaction problems, aka CSPs.)

\item. Farmer, Fox, Goose and Grain.
The FFGG problem, alternately known as the fox, goose, and bag of beans problem, is a river crossing puzzle usually stated as follows (https://en.wikipedia.org/wiki/Fox,\_goose\_and\_bag\_of\_beans\_puzzle ):

A farmer comes to a river bank with a fox, a goose, and a sack of grain.
He can cross over using a boat that holds himself and one of the three items at a time.
If the fox is left on one bank with the goose, it will eat the goose.
If the goose is left on one bank with the grain, it will eat the grain.
Can the farmer get all three items and himself across without anything being eaten?

Formulate the problem precisely as a state space.
Turn in an illustration of the state space diagram, showing which states are the initial states and which are reachable from each other.
Rather than just give the state space provided in the Wikipedia article, explain your derivation and the operations on this state space.

Answer the following: How many distinct states (legal/reachable or not are there), if we define each object as being on one bank or the other?
How many reachable states are there? How many different solutions starting from either side are there?
\end{enumerate}

\bigbreak

\textbf{Solution:}

i. 


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
































